Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2017-03-13 paper.tex
include several sections, as subsections, inside the methodology section
Added three costs matrices

\usepackage{graphics,subfigure}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

@@

@@

>>>>

\usepackage{graphics,subfigure}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{multirow}

@@

% maybe the following sections should be included inside the Methodology section, as subsections.

\begin{itemize}
\item Data preparation:

\item Select best base classifier:

\item Select best ensemble classifier:

\item Perform cost-sensitive analysis with best ensemble classifiers:

\item Evaluation and comparison:

@@

\begin{table}
\caption{Cost matrices for three different scenarios}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline 
\multicolumn{2}{|c|}{} & \multicolumn{14}{c|}{Actual}\tabularnewline
\hline 
\multicolumn{2}{|c|}{} & \multicolumn{4}{c|}{Cost matrix 1} & \multirow{6}{*}{} & \multicolumn{4}{c|}{Cost matrix 2} & \multirow{6}{*}{} & \multicolumn{4}{c|}{Cost matrix 3}\tabularnewline
\cline{1-6} \cline{8-11} \cline{13-16} 
\multicolumn{2}{|c|}{} & L & M & H & VH &  & L & M & H & VH &  & L & M & H & VH\tabularnewline
\cline{1-6} \cline{8-11} \cline{13-16} 
\multirow{4}{*}{Predicted} & L & 0 & 1 & 2 & 3 &  & 0 & 1 & 2 & 3 &  & 0 & 1 & 2 & 3\tabularnewline
\cline{2-6} \cline{8-11} \cline{13-16} 
 & M & 5 & 0 & 1 & 2 &  & 10 & 0 & 1 & 2 &  & 15 & 0 & 1 & 2\tabularnewline
\cline{2-6} \cline{8-11} \cline{13-16} 
 & H & 10 & 5 & 0 & 1 &  & 20 & 10 & 0 & 1 &  & 30 & 15 & 0 & 1\tabularnewline
\cline{2-6} \cline{8-11} \cline{13-16} 
 & VH & 15 & 10 & 5 & 0 &  & 30 & 20 & 10 & 0 &  & 45 & 30 & 15 & 0\tabularnewline
\hline 
\end{tabular}
\end{table}
